Code used to generate paper results : Database comparison and CT characteristics

### 2024-06-05 Paper_code-Database_Comparison.Rmd
Adapted database fig

upset_text_size <- c(1.5, 1.5, 1.5, 1.5, 1.8, 2)
 #c(intersection size title, intersection size tick labels, set size title, 
 # set size tick labels, set names, numbers above bars)
```

@@

upset_all_database <- fromList(all_database_gene_list)
upset(upset_all_database,
      nsets = 6,
      nintersects = 50,
      text.scale = upset_text_size)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/upset_all_lost.pdf"))
upset(upset_all,
      text.scale = upset_text_size)
dev.off()

pdf(file = paste0("figs/upset_all_databases.pdf"))
upset(upset_all_database,
      nsets = 6,
      nintersects = 50)
dev.off()
```

>>>>

upset_text_size <- c(1.5, 1.5, 1.5, 1.5, 2, 2)
 #c(intersection size title, intersection size tick labels, set size title, 
 # set size tick labels, set names, numbers above bars)
```

@@

upset_all_database <- fromList(all_database_gene_list)

upset_text_size_all <- c(1.5, 1.5, 1.5, 1.5, 2, 1)
 #c(intersection size title, intersection size tick labels, set size title, 
 # set size tick labels, set names, numbers above bars)
upset(upset_all_database,
      nsets = 6,
      nintersects = 50,
      text.scale = upset_text_size_all)

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/upset_all_lost.pdf"))
upset(upset_all,
      text.scale = upset_text_size)
dev.off()

pdf(file = paste0("figs/upset_all_databases.pdf"))
upset(upset_all_database,
      nsets = 6,
      nintersects = 50,
      text.scale = upset_text_size_all)
dev.off()
```
